Coherent optical association of a single molecule

### 2020-09-19 paper.tex
whitespace, regenerate pdf
Reference

Diverse species of fully quantum controlled  ultracod molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and the studies of ultracold chemistry.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules  below 1~mK~\cite{Norrgard2016}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the associations of ultracold atoms. 
%(any place to cite  molecular ion work?)

>>>>

Diverse species of fully quantum controlled  ultracod molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and the studies of ultracold chemistry.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules  below 1~mK~\cite{Norrgard2016}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the associations of ultracold atoms.
%(any place to cite  molecular ion work?)
